PERFORMANCE ANALYSIS PROBLEMS IN TSN NETWORKS

### 2020-06-14 draft.tex
Restructured and improved KNN part.

\section {Background}
TSN employs different standards that are beriefly reviewed here in order to understand the flow control within a node of a TSN network. Reader interested in a more detailed survery can consult \cite {ULL}.
\subsection{TSN Concepts}
A unicast or multicast connection from one end station (talker) to another end station (listener) is called as a \emph {flow}, or a \emph {stream}.

In \cite{ULL}, the TSN standards are classified under properties of the flow, such as flow synchronization, flow management, flow control and flow integrity. Performance analysis or schedulability although considers different standards associated with the flow holistically but it is more focussed on standards associated with the flow control. In the following we take a brief look on TSN flow control.
\subsubsection{Flow Control}
\begin{figure}
\centering
\includegraphics[width=3.5in]{TSNFlowControl}
\caption{Flow control at an output port employing TSN CBS and TAS with and without preemption}
\label{TSN_FlowControl}
\end{figure}
The flow control in general deals with the schedule of the flows in order to comply with the QoS requirements primarily latency. There are different standards that play their role in scheduling different classes of traffic in a TSN.

@@

IEEE 802.1Qbu \cite{IEEE802.1Qbu} introduces low priority traffic frame preemption with an overhead. The guard band here gets reduced to the shortest low priority frame fragment.

\section {Analysis}
As discussed, TSN employs broad range of standards aimed at different use-cases with stringent latency requirements. In the flow control in order to schedule a packet dynamically, the scheduling entity needs to determine the schedulability of the frame i-e the latency of scheduled packet should be less than the worst case latency for the traffic. In the presence of multitude TSN standards at a node the analysis to determine the schdulability becomes involved. In this section, we review three different techniques aimed at the timing analysis primarily latency of dynamic traffic of a network.

\subsection {ML Based Analysis}
This methodology significantly differs from the other techniques discussed here as it does not explore underlying mathematical timing analysis to determine schedulability of a configuration. The paper \cite{ML} develops a machine learning model to ascertain feasibility of different configurations of a real time ethernet network as available under TSN standards. It goes on to compare performance metric, i-e accuracy and computation time, of the developed model with two network calculus based models referred to as approximate and precise in the paper.

\subsubsection{Model}
Four TSN based configurations are considered while evaluating feasible configurations for a real time ethernet network given the traffic and their associate timing constraints. The configuration are named as FIFO, Manual, Concise Priority (CP8) and Manual with traffic shaping, for details consult \cite{ML}. The configuration are proposed while keeping TSN standards in mind while consorting to the standard static priority scheduling algorithms in order to compare the ML model results with so called “approximate analysis” and “precise analysis based off  \cite{8,9,37}.

A generic topology of network is given for which three classes of traffic is scheduled namely Audio, Video and Command and Control (C\&C). The ML model that is used to determine feasibility of a configuration is K Nearest Neighbors (KNN), K being an arbitrary number of neighbors. The learning complexity of the model is O(N), N being the training data set, as it only needs to store the training data set. Each member of training data set of length N, is D dimensional, D being the number of features of a configuration having maximum impact on the end result i-e if a particular configuration having certain values of D features is feasible to schedule or not. The decision sought from the ML model is binary i-e schedulable or not schedulable.
In the training phase of the model, the labelled training data is stored in an N x D array, for instance. The decision of the feasibility against these data indices is stored in a N dimensional array where entries 0 and 1 represent non-feasibility and feasibility respectively. Once a prediction against a new configuration, i-e a D dimensional data point, is sought from the ML model, an L2 norm of the data point is calculated from the N data points stored as training data set and K closest neighbors of the data point are identified. Based on majority voting of feasibility status of K neighbors, the decision of feasible or not feasible is taken against the new configuration. Four such models are developed against the solutions proposed earlier. The computational complexity here is of order of O(NKD) for each new configuration.
In order to have accurate prediction, the training data set should be sufficient to populate D dimensional space of data points adequately. The trade off here is clear; more features of a configuration mean more apt characterization of the configuration; however, this also implies that more data points are needed to populate now higher dimensional space of the data set in order to have accurate predictions. This phenomenon is referred to as curse of dimensionality.
In the ML model developed in the \cite{ML}, following five features of a configuration are selected based on the empirical results: the number of critical flows, the number of audio flows, the number of video flows, the maximum load of the network and Gini Index. Gini Index \cite{GINI} is a quantitative characterization of unbalancedness of link loads.
\subsubsection{Results}
The training data set is generated by labelling randomly generated data of the given topology by the accurate analysis in order to avoid false negatives. The hyperparameters such as K neighbors, K fold cross validation are fine-tuned by experiments.
A training data set of N=5200 was deemed optimum against the accuracy, where any increases in N afterwards plateaued the accuracy curve.
As can be seen in Table 2 of \cite{ML} the overall accuracy reduces with increasingly complex model. True Positive Rate (TPR) captures the percentage of accurate prediction of the overall prediction deemed to be feasible by the model. The TNR is just the converse of TPR. The lower percentage of TPR in the case of FIFO is correlated by Kappa Index and F Index. The reason behind that is low coverage of D dimensional space for the case of feasible solutions. As most of the training data set contained not feasible solutions indicated by F index for the case of FIFO scheduling.
The figure 6 in \cite{ML} shows the comparison of the performance of ML model against the “approximate” and “accurate” analysis in the case of Manual Scheduling, the accuracy of the model is slightly worse than the two other two analysis. However, there is a significant difference of computation time only for the case 10\^6 TSN configurations.
The table 3 of \cite{ML} summarizes the accuracy result and make a comparison against the other two analyses. The interesting point to note is that the analyses do not yield False Positive Rate as opposed to the ML model, which might indicate potential room of improvement in the Approx. analysis as it is pessimistic. For the case of CP8 there is an improvement of overall accuracy in the case of ML model
\subsubsection{Conclusion}
The paper was premised around infeasibility of computational time in the case of accurate analysis however the choice of ML model is not consistent with the premise, since the prediction time of the model will increase linearly with the training data set.
 Another potential improvement could be feature selection, there is no evidence of different features selection for different schedulability in the paper, as can be seen in table that the accuracy has degraded with more complicated solution. Perhaps different features selection for each solution would customize the characterization of a configuration with respect to that solution and may drive the overall accuracy higher.

Furthermore, it does not provide a worst-case estimate on the latencies which remains a major draw back even for a relatively accurate model. As it does not guarantee a worst-case latency, hence it is best suitable as a verification method for the timing constraints.

>>>>

\section {Background}
TSN employs different standards that are beriefly reviewed here in order to understand the flow control within a node of a TSN network. Reader interested in a more detailed survery can consult \cite {ULL}.
\subsection{TSN}
A unicast or multicast connection from one end station (talker) to another end station (listener) is called as a \emph {flow}, or a \emph {stream}.

In \cite{ULL}, the TSN standards are classified under properties of the flow, such as flow synchronization, flow management, flow control and flow integrity. Performance analysis or schedulability although considers different standards associated with the flow holistically but it is more focussed on standards associated with the flow control. In the following we take a brief look on TSN flow control.
\subsubsection{Flow Control}
\begin{figure}
\centering
\includegraphics[width=3.5in]{TSNFlowControl}
\caption{Flow control at an output port employing TSN CBS and TAS with and without preemption}
\label{TSN_FlowControl}
\end{figure}
The flow control in general deals with the schedule of the flows featuring QoS strategies such as static priority scheduling and traffic shaping. There are different standards that play their role in scheduling different classes of traffic in a TSN.

@@

IEEE 802.1Qbu \cite{IEEE802.1Qbu} introduces low priority traffic frame preemption with an overhead. The guard band here gets reduced to the shortest low priority frame fragment. See Fig. \ref{TSN_FlowControl} for an example of flow control at an output port, gates of each queue are being controlled by GCL.

\section {Analysis}
As discussed, TSN employs broad range of standards aimed at different use-cases with stringent latency requirements. In the presence of multitude of TSN standards the analysis to determine the schdulability becomes involved. In this section, we review three different techniques aimed at the timing analysis of dynamic traffic of a network.

\subsection {ML Based Analysis}
The methodology presented in \cite{ML} significantly differs from the other techniques discussed here, it does not explore underlying timing analysis to determine schedulability of a new configuration rather it makes decision based on its similarity with precomputed configurations.

\subsubsection{Model}
In order to evaluate feasibility of a new application, it is evaluated against four possible TSN configurations (or solutions). The Four TSN configurations are FIFO, Manual, Concise Priority (CP8) and Manual with traffic shaping, for details see \cite{ML}. The configurations are compatible with the standard static priority scheduling algorithms in order to compare the ML model results with so called “approximate analysis” and “precise analysis'' based off  \cite{8,9,37}.
\begin{figure}
\centering
\includegraphics[width=3.5in]{KNN}
\caption{A toy KNN model for two features, the new configuration will be characterized as `feasible' for $K<6$}
\label{KNN}
\end{figure}

A generic topology of network is given for which three classes of traffic is scheduled namely Audio, Video and Command and Control (C\&C). The ML model that is used to determine feasibility of a configuration is K Nearest Neighbors (KNN). Fig. \ref{KNN} shows a KNN model for two features X and Y. In order to classify a new configuration (marked as `?') an L2 norm is taken to determine dominant label of nearest neighbors as shown by the circles for the case of K=1 and 2.

In the ML model developed in \cite{ML}, following five features (D=5) of a configuration are selected based on the empirical results: the number of critical flows, the number of audio flows, the number of video flows, the maximum load of the network and Gini Index. Gini Index \cite{GINI} is a quantitative characterization of unbalancedness of link loads. The decision sought from the model is binary i-e if a given point in a D dimensional space connotes to either a feasible or an infeasible configuration.
\subsubsection{Results}
The training data for each solution is generated by labelling randomly generated data of the given topology by the results of `accurate analysis' \cite{8,9,37} which are considered to be 100\% accurate. A training data set of N=5200 was deemed optimum.
The overall accuracy of the model reduces with increasingly complex solution. For the case of FIFO scheduling the model is a bit biased towards infeasible predictions. The reason behind that is most of the training data set contained not feasible solutions.
The accuracy of the model is worst than `approximate' analysis on average, there is a significant difference of computation time only for the case $10^6$ TSN configurations.
%The figure 6 in \cite{ML} shows the comparison of the performance of ML model against the “approximate” and “accurate” analysis in the case of Manual Scheduling, the accuracy of the model is slightly worse than the two other two analysis. However, there is a significant difference of computation time only for the case 10\^ 6 TSN configurations.
%The table 3 of \cite{ML} summarizes the accuracy result and make a comparison against the other two analyses. The interesting point to note is that the analyses do not yield False Positive Rate as opposed to the ML model, which might indicate potential room of improvement in the Approx. analysis as it is pessimistic. For the case of CP8 there is an improvement of overall accuracy in the case of ML model
\subsubsection{Conclusion}
The paper was premised around infeasibility of computational time in the case of accurate analysis however the choice of ML model is not consistent with the premise, since the prediction time of the model (complexity of the order of O(NKD)) will increase linearly with the training data set.
Another potential improvement could be feature selection, there is no evidence of different features selection for different schedulability in the paper, as indicaed earlier the accuracy has been degraded with more complicated solution. Perhaps different features selection for each solution would customize the characterization of a configuration with respect to that solution and may drive the overall accuracy higher.

Furthermore, it does not provide a worst-case estimate on the latencies which remains a major draw back even for a relatively accurate model. As it does not guarantee a worst-case latency.
